---
title: "Untitled"
author: "Rene Pineda"
date: "June 11, 2018"
output: html_document
---

#MSDS 6371 Project 1

## Setup and Loading packagges
```{r setup, echo=FALSE}

#Set up working directory
setwd("E:/Bibliotecas/Documents/Data Science/SMU/MSDS 6372/AppliedStatsProject1")

#Load the data
train <- read.csv("train.csv")
test <- read.csv("test.csv")

#Inspect the data
dim(train)
str(train)

library(sqldf) # Used for manipulating the data frames using SQL
library(glmnet) # Used for...
library(caret) # Used for...
library(forcats) # Used for...
library(olsrr) # Used for creating the foward, backward, and stepwise models
library(tidyr) #Used for creating some of the plots
library(ggplot2) #Used for creating some of the plots
library(corrplot) #Used to create the correlation matrix
```



## Data cleaning and preparation

```{r data preparation, echo=FALSE}

#This shows us what is null
sapply(train, function(x) sum(is.na(x)))

#upon inspecton, the following variables have missing information:
#LotFrontage, Alley, MasVnrType, MasVnrArea, BsmtQual, BstCond, BsmtExposure, BsmtFinType1, BsmtFinType2,
#FireplaceQu, GarageType, GarageYrBlt, GarageFinish, GarageCond, Fence, MiscFeature, PoolQC

#Adding sale price to the test set for combining
test$SalePrice <- 0  

#Join the train and test sets for preprocessing
data <- rbind(train, test)

#Converting values to NULL in the following variables tha will not be used
data$MiscFeature <- NULL # Missing value in 96.4% of observations
data$Alley <- NULL # Missing value in 93.2% of observations
data$PoolQC <- NULL # Missing value in 99.7% of observations

#Variables with values as NA
NAFeatures = names(which(colSums(is.na(data))>0))

#Get the median lot frontage and update where NA
median(train$LotFrontage, na.rm = TRUE)  # This ends up being 69.  Going to update the NA 

data$LotFrontage[is.na(data$LotFrontage)] <-69

#If NA for GarageYrBlt, then set to YearBuilt of house
data$GarageYrBlt[is.na(data$GarageYrBlt)] <-  as.integer(data$YearBuilt)

#Create vectors of Variables with missing observations and variables with zero values
missingObs = c("MSZoning", "MasVnrType", "Utilities", "Exterior1st", "Exterior2nd", "SaleType")
effZero = c("LotFrontage", "MasVnrArea", "BsmtFinSF1", "BsmtFinSF2", "BsmtUnfSF", "TotalBsmtSF","GarageCars", "GarageArea", "BsmtFullBath", "BsmtHalfBath")

# Get Effectively Absent category by excluding other categories from varsWithNA
effAbsent = NAFeatures[!NAFeatures %in% missingObs]
effAbsent = effAbsent[!effAbsent %in% effZero]
effAbsent = effAbsent[!effAbsent %in% c("Functional")]

# Function for replacing NAs in nominal and ordinal variables
replaceNAfactor = function(data.col, factorString){
  char.col <- as.character(data.col)
  char.col[which(is.na(data.col))] <- factorString
  as.factor(char.col)
}

# Replace NAs with None in Effectively Absent category
for (i in 1:ncol(data)){
  if(names(data[i]) %in% effAbsent){
    data[,i] <- replaceNAfactor(data[,i], "None")}
}

# Replace NAs with MissingObs in Missing Observations category
for (i in 1:ncol(data)){
  if(names(data[i]) %in% missingObs){
    data[,i] <- replaceNAfactor(data[,i], "MissingObs")}
}

# Replace NAs with 0 in Effectively Zero category
for (i in 1:ncol(data)){
  if(names(data[i]) %in% effZero)
    data[is.na(data[,i]),i] <- 0
}

data$Functional <- replaceNAfactor(data$Functional, "Typ")

#Checking that we corrected for NAs
sapply(data, function(x) sum(is.na(x)))

#Resplitting train and test
xtrain <- sqldf("select * from data where SalePrice <> 0")
ytrain <- sqldf("select SalePrice from data where SalePrice <> 0")
names(ytrain) <- c("SalePrice")

xtrain$SalePrice <- NULL

xtest <- sqldf("select * from data where SalePrice = 0")

xtest$SalePrice <- NULL
```

## Some exploratory Analysis


```{r Corr Matrix and Scatterplots, echo=FALSE}
#Correlation matrix
#The following variables will be included in the matrix: Lot Frontage, Lot Area, Year Built, Year Remod/Add, 
#Mas Vnr Area, Bsmt Fin SF 1, BsmtFin SF 2, Bsmt Unf SF, Total Bsmt SF, 1st Flr SF, 2nd Flr SF, Low Qual Fin SF,
#Gr Liv Area, Garage Area, Wood Deck Sf, Open Porch SF, Enclosed Porch, 3-Ssn Porch, Screen Porch, Pool Area, 
#Misc Val, Yr Sold, Sale Price

#Choose only these variables:
numericvars <- xtrain[,c(4,5,19,20,26,34,36,37,38,43,44,45,46,62,66,67,68,69,70,71,73,75)]
nonnumericvars <- xtrain[,-c(4,5,19,20,26,34,36,37,38,43,44,45,46,62,66,67,68,69,70,71,73,75)]
corrvar <- cbind(numericvars,ytrain)

#Create the correlation matrix

N <- cor(corrvar, use = "complete.obs")
corrplot(N, method = "number", number.cex = 0.5, tl.cex = 0.7)           

#Create the scatterplots

#Function to create the scatterplots
scatterplots <- cbind(xtrain, ytrain)

makeScatterplots <- function(dataframe,x.variable){
  print(ggplot(data = dataframe) + 
    geom_point(mapping = aes(x = scatterplots[,x.variable], y = SalePrice), color = "dodgerblue3" ) +
    scale_y_continuous(labels = scales::dollar) +
    labs(x = (names(scatterplots[x.variable]))))
  }

#Create the scatterplots you're interested in by changing the variable numbers in the FOR statement
for (variable in c(2,75,25,6,8,14,29)){
  makeScatterplots(scatterplots,variable)
}
```

##Regression Models

So far we've created four regression models
* Initial model with all variables: modelfit1
* LASSO model
* Forward selection model using p-values as criteria: modelfoward
* Backward selection model using p-values as criteria: modelbackward
* Stepwise selection model using p-values as criteria: modelstepwise

```{r Regression models, echo=FALSE}
#Running an initial regression model with all the data
modelfit1 <- lm(ytrain$SalePrice ~ ., data = xtrain[,-1])
summary(modelfit1)
#R^2 is .937
summary(modelfit1)$adj.r.squared

#Lasso Model

`%ni%` <- Negate(`%in%`)

x = model.matrix(ytrain$SalePrice~., data = xtrain[,-1]) 
y = (ytrain$SalePrice)

cv.out <- cv.glmnet(x,y,alpha = 1)
plot(cv.out)
bestlambda <- cv.out$lambda.1se

c<- coef(cv.out, s = bestlambda, extract = TRUE)
inds <- which(c!=0)
variables <- row.names(c)[inds]
variables <- variables[variables %ni% ('Intercept')]
variables

#Forward selection model
model <- lm(ytrain$SalePrice ~ ., data = xtrain)
modelforward <- ols_step_forward_p(model)
modelforward
plot(modelforward)

#Backward Selection model
#Code does not work as desired
# modelbackward <- ols_step_backward_p(model)
# modelbackward
# plot(modelbackward)

#Stepwise Selection model
#Code does not work as desired
#modelstepwise <- ols_step_both_p(model)
#modelstepwise
#plot(modelstepwise)
```

##Pending tasks

* Run several models from all the selection processes. Check why the olsrr package does not produce the models
* Enter interaction terms (ex:  GarageYrBuilt * GarageCars * GarageArea )
* Create table comparing comparing AIC or R^2 from all models, and make decision
* Perform the 2-way ANOVA analysis for the second part of the project assignment